### 2018-10-02 paper/paper.tex
initial commit

\documentclass[dvips,mnsc]{informs3}
% [citeauthoryear]

\OneAndAHalfSpacedXI % current default line spacing
%%\OneAndAHalfSpacedXII
%%\DoubleSpacedXII
%%\DoubleSpacedXI

% If hyperref is used, dvi-to-ps driver of choice must be declared as
%   an additional option to the \documentstyle. For example
%\documentclass[dvips,mnsc]{informs3}      % if dvips is used
%\documentclass[dvipsone,mnsc]{informs3}   % if dvipsone is used, etc.

% Private macros here (check that there is no clash with the style)

% --------------------

% \usepackage[table]{xcolor}
% \usepackage{xcolor}
% \usepackage[utf8x]{inputenc}
% \usepackage{listings}
% \usepackage{amsmath,amssymb}
% \usepackage[noend]{algpseudocode}
% \usepackage{stmaryrd}
% \usepackage{listings}
% \usepackage{algorithm}
% \usepackage{array}
% \usepackage{textcomp}
% \usepackage{pifont}
% \usepackage{bbding}
% \usepackage{comment}
% \usepackage{graphicx}
% \usepackage{paper}
% \usepackage[svgpath=figures/]{svg}
% \usepackage[labelfont=bf]{caption}
% \captionsetup[table]{skip=5pt}

% \usepackage{academicons}
% \usepackage{cite}
% \usepackage[hidelinks,
% plainpages=false,
% pdftitle={
%   The Lead Time Syndrome
% },
% pdfauthor={Manuel Schneckenreither and Stefan Haeussler},
% pdfsubject={  The Lead Time Syndrome},
% pdfkeywords={production planning, order release, lead time syndrome, formalisation, detection,
%   operations research},
% ]{hyperref}

% \usepackage{url}

\newcommand\SH[2][r]{\ifx t#1 \textcolor{green!50!black}{[\textbf{SH:} #2]}
  \else \begin{center}\textcolor{green!50!black}{\textbf{SH:} #2} \end{center} \fi}

\newcommand\MS[2][r]{\ifx t#1 \textcolor{blue}{[\textbf{MS:} #2]}
  \else \begin{center}\textcolor{blue}{\textbf{MS:} #2} \end{center} \fi}

\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
% --------------------

% Natbib setup for author-year style
\usepackage{natbib}
 \bibpunct[, ]{(}{)}{,}{a}{}{,}%
 \def\bibfont{\small}%
 \def\bibsep{\smallskipamount}%
 \def\bibhang{24pt}%
 \def\newblock{\ }%
 \def\BIBand{and}%

%% Setup of theorem styles. Outcomment only one.
%% Preferred default is the first option.
\TheoremsNumberedThrough     % Preferred (Theorem 1, Lemma 1, Theorem 2)
%\TheoremsNumberedByChapter  % (Theorem 1.1, Lema 1.1, Theorem 1.2)
\ECRepeatTheorems

%% Setup of the equation numbering system. Outcomment only one.
%% Preferred default is the first option.
\EquationsNumberedThrough    % Default: (1), (2), ...
%\EquationsNumberedBySection % (1.1), (1.2), ...

% For new submissions, leave this number blank.
% For revisions, input the manuscript number assigned by the on-line
% system along with a suffix ".Rx" where x is the revision number.
\MANUSCRIPTNO{}

%%%%%%%%%%%%%%%%
\begin{document}
%%%%%%%%%%%%%%%%

% Outcomment only when entries are known. Otherwise leave as is and
%   default values will be used.
%\setcounter{page}{1}
%\VOLUME{00}%
%\NO{0}%
%\MONTH{Xxxxx}% (month or a similar seasonal id)
%\YEAR{0000}% e.g., 2005
%\FIRSTPAGE{000}%
%\LASTPAGE{000}%
%\SHORTYEAR{00}% shortened year (two-digit)
%\ISSUE{0000} %
%\LONGFIRSTPAGE{0001} %
%\DOI{10.1287/xxxx.0000.0000}%

% Author's names for the running heads
% Sample depending on the number of authors;
% \RUNAUTHOR{Jones}
% \RUNAUTHOR{Jones and Wilson}
% \RUNAUTHOR{Jones, Miller, and Wilson}
% \RUNAUTHOR{Jones et al.} % for four or more authors
% Enter authors following the given pattern:
\RUNAUTHOR{Schneckenreither and Haeussler}
%\RUNAUTHOR{}

% Title or shortened title suitable for running heads. Sample:
% \RUNTITLE{Bundling Information Goods of Decreasing Value}
% Enter the (shortened) title:
\RUNTITLE{The Lead Time Syndrome}

% Full title. Sample:
% \TITLE{Bundling Information Goods of Decreasing Value}
% Enter the full title:
\TITLE{A Formalisation of the Lead Time Syndrome}

% Block of authors and their affiliations starts here:
% NOTE: Authors with same affiliation, if the order of authors allows,
%   should be entered in ONE field, separated by a comma.
%   \EMAIL field can be repeated if more than one author
\ARTICLEAUTHORS{%
  \AUTHOR{Manuel Schneckenreither% \orcidID{0000-0002-4812-4665}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  \EMAIL{manuel.schneckenreither@uibk.ac.at}} %, \URL{}}

  \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
  }
  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
  \EMAIL{stefan.haeussler@uibk.ac.at}}
} % end of the block

\ABSTRACT{%
  TODO
% Enter your abstract
}%

% Sample
%\KEYWORDS{deterministic inventory theory; infinite linear programming duality;
%  existence of optimal policies; semi-Markov decision process; cyclic schedule}

% Fill in data. If unknown, outcomment the field
\KEYWORDS{production planning, order release, lead time syndrome, formalisation, operations
  research}
\HISTORY{ % This paper was first submitted on April 12, 1922 and has been with the authors for 83 years
  % for 65 revisions.
}

\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Samples of sectioning (and labeling) in MNSC
% NOTE: (1) \section and \subsection do NOT end with a period
%       (2) \subsubsection and lower need end punctuation
%       (3) capitalization is as shown (title style).
%
%\section{Introduction.}\label{intro} %%1.
%\subsection{Duality and the Classical EOQ Problem.}\label{class-EOQ} %% 1.1.
%\subsection{Outline.}\label{outline1} %% 1.2.
%\subsubsection{Cyclic Schedules for the General Deterministic SMDP.}
%  \label{cyclic-schedules} %% 1.2.1
%\section{Problem Description.}\label{problemdescription} %% 2.

% Text of your paper here

\section{Introduction}
\label{sec:introduction}

\section{The Lead Time Syndrome}
\label{sec:The_Lead_Time_Syndrome}

Zumindest durschnittlich gleichbleibende Freigabemenge bei über die Zeit steigender EDT (oder
eventuell die Warteschlangenlänge [von Stage 1]).

\begin{definition}
  The \emph{Lead Time Syndrome} is defined as
\end{definition}

% *Informelle Definition LTS_+*

\section{Experimental Evidence}
\label{sec:Experimental_Evidence}

\section{Conclusion}
\label{sec:Conclusion}

\bibliography{references}
\bibliographystyle{plainnat}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-10-03 paper/paper.tex
added references

@@
 % \usepackage{graphicx}
-% \usepackage{paper}
+\usepackage{paper}
 % \usepackage[svgpath=figures/]{svg}
@@
 
+Lead Time Syndrome (LTS)
+
 \section{The Lead Time Syndrome}
 \label{sec:The_Lead_Time_Syndrome}
+
+In this section we present a formalisation of the \LTS{}. It is straightforward to implement the
+presented methods to establish a \LTS{} detection system. We follow the notation established
+by~\cite{selccuk2013adaptive}.
+
+\subsection{Single-Stage Manufacturing System}
+\label{subsec:Single-Stage_Manufacturing_System}
+
+Consider a single product one-stage manufacturing system that releases orders from the order pool
+into the production system by an external mechanism. We denote the demand rate at time
+$t \geqslant 0$ as $\dr{t}$, and the demand for the item during the period defined by timestamps
+$t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$. Similarly we denote the order release
+rate as $\rr{t}$ and the releases within a period as $\ri{t_{1}}{t_{2}}$. Usually
+
+\begin{definition}
+
+  The overall queue length
+
+\end{definition}
 
@@
 % *Informelle Definition LTS_+*
+
+\subsection{Multi-Stage Manufacturing System}
+\label{subsec:Multi-Stage_Manufacturing_System}
+
+We now lift the established metric to multi-stage manufacturing systems.
 
@@
 \end{document}
+
+% --------------------
 %%% Local Variables:

### 2018-10-03 paper/paper.tex
update paper; LTS cycle; LTS name; started over time part

@@
-\documentclass[dvips,mnsc]{informs3}
+\documentclass[mnsc]{informs3}
 % [citeauthoryear]
@@
 % --------------------
-
+\usepackage[utf8x]{inputenc}
 % \usepackage[table]{xcolor}
 % \usepackage{xcolor}
-% \usepackage[utf8x]{inputenc}
 % \usepackage{listings}
@@
 
-Lead Time Syndrome (LTS)
+Introduce abbreviations:
+\begin{itemize}
+\item Lead Time Syndrome (\LTS{})
+\item Work-in-process (\WIP{})
+\end{itemize}
+
+Related literature \MS[t]{Cite!} argues that the lead time syndrome can only occur (i) if a lead
+time is set dynamically and nonreciprocal according to the current \WIP{}-level and (ii) the order
+releases monotonically depend on this lead time. In a practical point of view this assumption is
+correct, however theoretically the interconnection between \WIP{}-level and number of releases is
+not needed to infer this systematic releasing misbehavior.
+
+\begin{proof}{Proof}
+  Consider a manufacturer with constant demand and an order release mechanism which strictly
+  increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
+  the release decision does neither depend on the flow time nor lead time. However, considered over
+  time this leads to a monotonically increasing \WIP{}-level which again leads to a monotonically
+  increasing lead time.\qed
+\end{proof}
+
+% \MS{name clash: LEAD TIME Syndrome with no LEAD TIME?}
+Despite this theoretical observation the name lead time syndrome may be under question. However, as
+in cases as given in the proof above the lead time follows the order release decisions and in
+practice order releases are usually determined by the lead time (or flow time) the wording can be
+considered as appropriate.
 
@@
 
-In this section we present a formalisation of the \LTS{}. It is straightforward to implement the
-presented methods to establish a \LTS{} detection system. We follow the notation established
-by~\cite{selccuk2013adaptive}.
+In this section we present a formalisation of the \LTS{}.
+%
+\MS[t]{TODO} The section is split into two
+parts. First we will present the method for single-stage manufacturers, before considering more
+stages.
+%
+It is straightforward to implement the presented methods to establish a \LTS{} detection system, see
+Section~\ref{sec:Experimental_Evidence}. We follow the notation established
+by~\cite{selccuk2013adaptive} to ease readability.
 
@@
 
-Consider a single product one-stage manufacturing system that releases orders from the order pool
-into the production system by an external mechanism. We denote the demand rate at time
-$t \geqslant 0$ as $\dr{t}$, and the demand for the item during the period defined by timestamps
-$t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$. Similarly we denote the order release
-rate as $\rr{t}$ and the releases within a period as $\ri{t_{1}}{t_{2}}$. Usually
+Consider a single product one-stage flow-shop manufacturing system that releases orders from the
+order pool into the production system by an external mechanism.
+%
+Usually the orders are released based on the observed (average) flow time of the last finished
+orders. However, our method does not presuppose such an interdependence for detecting the lead time
+syndrome as it works directly on (parts of) the \WIP{}-level of the system.
+%
+% Intuitively the method works as
+% follows. By measuring the change of the average \WIP{}-level over time and comparing this to the
+% average releases into the system it can infer the desired property.
+%
+We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
+the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
+Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
+$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
+orders are appended according to a given routing and from there handed over to the work-station if
+only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
+processing of unique orders with non-shared queues in the setup. In case of shared queues in this
+single item setup the work-station shall be considered as a single work-station. The size of a queue
+$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.
 
@@
 
-  The overall queue length
+  The queue size $\size{\Q_{i}}$ of stage $i$ is defined as
+  $\size{\Q_{i}} = \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
+  $i$. Note that in this subsection we set $i=1$.
 
 \end{definition}
+
+As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
+considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
+demand. It can clearly not be considered a lead time syndrome if the releases just depict the
+demand. However
+
+and therefore
+specifies the
 

### 2018-10-03 paper/paper.tex
Usage of observation.

@@
 Despite this theoretical observation the name lead time syndrome may be under question. However, as
-in cases as given in the proof above the lead time follows the order release decisions and in
-practice order releases are usually determined by the lead time (or flow time) the wording can be
-considered as appropriate.
+in cases like the one given in the proof above the lead time follows the order release decisions and
+in practice order releases are usually determined by the lead time (or flow time), the wording can
+be considered as appropriate.
+%
+Nonetheless, our method is based on this observation. First we do not consider the lead time as
+input variable to the method, then we do not suppose an interconnection between the \WIP{}-level
+with the release decision procedure, and finally we do not restrict our method on any particular
+order release pattern.
 
@@
 orders. However, our method does not presuppose such an interdependence for detecting the lead time
-syndrome as it works directly on (parts of) the \WIP{}-level of the system.
+syndrome as it works directly on (parts of) the \WIP{}-level of the system. Thus our approach is
+also able to observe systematic releasing misbehavior, referred to as \LTS{}, which do not consider
+the lead time as depended variable for the release decisions.
 %

### 2018-10-03 paper/paper.tex
demand definiert

@@
 As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
-considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
-demand. It can clearly not be considered a lead time syndrome if the releases just depict the
-demand. However
+considered as time factor in the formulation of the lead time syndrome. To clarify, consider a
+seasonal demand. It can clearly not be considered a lead time syndrome if the releases just depict
+the demand.
 
-and therefore
-specifies the
+Let the periodic demand be given by $\di{t}{t+1} = \dmean(\frac{t+t+1}{2}) + \epsilon$,
+where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
+at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with standard deviation $\sigma$.
+
+\begin{example}
+  In case of a constant demand, $\dmean$ maps to a constant value, whereas in a seasonal demand $f$
+  might be the sine-function. In most cases we expect the random variable to be drawn from the
+  standard distribution: $\X \sim \N{0}{\sigma^{2}}$.
+\end{example}
+
+- je mehr variation im demand desto länger die zeit
+
+and therefore specifies the
 

### 2018-10-03 paper/paper.tex
update paper

--- 2018-10-03 paper/paper.tex
@@
 %
-We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$, and the demand for the item during
-the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as $\di{t_{1}}{t_{2}}$.
-Similarly we denote the order release rate as $\rr{t}$ and the releases within a period as
-$\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which released
-orders are appended according to a given routing and from there handed over to the work-station if
-only if the work-station is empty and the order is at the head of the queue. Thus we allow parallel
-processing of unique orders with non-shared queues in the setup. In case of shared queues in this
-single item setup the work-station shall be considered as a single work-station. The size of a queue
-$\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.
+We denote the demand rate at time $t \geqslant 0$ as $\dr{t}$ \MS[t]{rates needed?}, and the demand
+for the item during the period defined by timestamps $t_{2} \geqslant t_{1} \geqslant 0$ as
+$\di{t_{1}}{t_{2}}$. Similarly we denote the order release rate as $\rr{t}$ and the releases within
+a period as $\ri{t_{1}}{t_{2}}$. Each work-station $i$ is equipped with a queue $\q_{i}$ on which
+released orders are appended according to a given routing and from there handed over to the
+work-station if only if the work-station is empty and the order is at the head of the queue. Thus we
+allow parallel processing of unique orders with non-shared queues in the setup. In case of shared
+queues in this single item setup the work-station shall be considered as a single work-station. The
+size of a queue $\size{\q_{i}} \geqslant 0$ is given by the number of orders within the queue.
 
@@
 
-  The queue size $\size{\Q_{i}}$ of stage $i$ is defined as
-  $\size{\Q_{i}} = \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
+  The \emph{queue size} $\size{\Q_{i}}$ of stage $i$ is defined as
+  $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
   $i$. Note that in this subsection we set $i=1$.
@@
 As the demand may vary over time, e.g.~in a seasonal pattern or simply by some variance, it must be
-considered as time factor in formulation of the lead time syndrome. To clarify, consider a seasonal
-demand. It can clearly not be considered a lead time syndrome if the releases just depict the
-demand. However
+considered as time factor in the formulation of the lead time syndrome. To clarify, consider a
+seasonal demand. It can clearly not be considered a lead time syndrome if the releases just depict
+the demand.
 
-and therefore
-specifies the
+\MS{maybe use continuous representation below?}
+
+Let the periodic demand be given by $\di{t}{t+1} = \max(0,\dmean(\frac{t+t+1}{2}) + \epsilon)$,
+where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
+at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with mean $0$ and standard deviation
+$\sigma$.
+
+\begin{example}
+  In case of a constant demand, $\dmean$ maps to a constant value, whereas for a seasonal demand $f$
+  could be the sine-function.
+  % In most cases we expect the random variable to be drawn from the
+  % standard distribution $\X \sim \N{0}{\sigma^{2}}$ and in case of a discrete demand space applying
+  % the nearest integer function.
+\end{example}
+
+% \MS{needed at all? we got the variance. But the max operator is used?}
+% \begin{definition}
+%   We define the \emph{standardised demand} $\dl{t}$ with time $t \geqslant 0$ as $\dl{t} \defsym
+%   \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the demand to
+%   be able to investigate the deviations solely.
+%   % \begin{align*}
+%   %   \dl{t} \defsym
+%   %   \begin{cases}
+%   %     1 + \epsilon & \text{iff }\dmean(\frac{2t+1}{2}) = 0\\
+%   %     \dmean^{-1}(\frac{2t+1}{2}) \cdot \dmean(\frac{2t+1}{2}) + \epsilon & \text{otherwise}
+%   %   \end{cases}
+%   %   \tpkt
+%   % \end{align*}
+%   % Note that $\dmean(\cdot)$ is a scalar value and thus the inverse $\dmean^{-1}(\cdot)$ exists
+%   % unless the mean demand is $0$.
+% \end{definition}
+% The standardised demand allows us to extract useful information from the deviations of the
+
+We use the standard deviation $\sigma$ of the random variable $\X$ as measure for estimating the
+time span being considered in our model. Recall that the standard deviation measures the expected
+deviation of the mean in orders for one period.
+%
+Futhermore,... \MS[t]{seasonal stuff}
+%
+
+\begin{definition}
+  We define the time span $\ts$ of the manufacturing system under investigation as
+  \begin{align*}
+    \ts \defsym \MS[t]{\text{seasonal stuff todo}} + \z \cdot 2 \sigma \tcom
+  \end{align*}
+  where $\z$ is a parameter.
+\end{definition}
+
+- je mehr variation im demand desto länger die zeit
 

### 2018-10-04 paper/paper.tex
improvement of time span definition

@@
 
-Let the periodic demand be given by $\di{t}{t+1} = \max(0,\dmean(\frac{t+t+1}{2}) + \epsilon)$,
-where $\dmean$ is a function which maps any given time $t \geqslant 0$ to the expected mean demand
-at time $t$ and $\epsilon$ is drawn from a random variable $\X$ with mean $0$ and standard deviation
-$\sigma$.
+\begin{definition}
+  The \emph{periodised demand} $\dper{p}$ for any period $p \in \Nat$ is given by
+  $\dper{p} = \max(0,\dmean(\frac{p+p+1}{2}) + \epsilon) = \di{p}{p+1}$, where $\dmean$ is a
+  function which maps any given period to the expected mean demand at this period and $\epsilon$ is
+  drawn from a random variable $\X$ with mean $0$ and standard deviation $\sigma$. Note that $f$
+  must not necessarily be continuous.
+  % Note that the periodised demand is only defined over natural numbers, which describe the current
+  % period.
+\end{definition}
 
 \begin{example}
-  In case of a constant demand, $\dmean$ maps to a constant value, whereas for a seasonal demand $f$
-  could be the sine-function.
+  In case of a constant demand, $\dmean$ maps to a constant value and $\epsilon = 0$, whereas for a
+  seasonal demand $f$ in a continuous space one may use the sine-function and
+  $\X \sim \N{0}{\sigma^{2}}$.
+  %
+  \MS[t]{maybe refer to inventory control, as there $\N{0}{\cdot}$ is also used?}
+
   % In most cases we expect the random variable to be drawn from the
@@
 
+In practise the available demand data is used to infer the function $\dmean$ and the value for
+$\sigma$. This could be done using regression and statistical analyses. Therefore, in hereafter
+these values are expected to be known.
+
 % \MS{needed at all? we got the variance. But the max operator is used?}
 % \begin{definition}
-%   We define the \emph{standardised demand} $\dl{t}$ with time $t \geqslant 0$ as $\dl{t} \defsym
-%   \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the demand to
-%   be able to investigate the deviations solely.
+%   We define the \emph{mean deviation demand} $\ddev{t}$ with time $t \geqslant 0$ as
+%   $\ddev{t} \defsym \di{t}{t+1} - \dmean(\frac{2t+1}{2})$. That is we subtract the mean from the
+%   demand to be able to investigate the deviations solely.
 %   % \begin{align*}
-%   %   \dl{t} \defsym
+%   %   \ddev{t} \defsym
 %   %   \begin{cases}
@@
 
-We use the standard deviation $\sigma$ of the random variable $\X$ as measure for estimating the
-time span being considered in our model. Recall that the standard deviation measures the expected
-deviation of the mean in orders for one period.
+The higher the standard deviation of the demand, the more likely it is to find high fluctuations in
+the release pattern. Thus, the scaled deviations in the demand specify a natural lower-bound of
+release decisions to consider in the analysis of the \LTS{}.
+%
+Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
+demand as measure for determining the time span being considered. Recall that the standard deviation
+measures the expected deviation of the mean in orders.
+%
+%
+% Thus, $2 \sigma$ specify the (minimum) expected deviation of the demand and thus also the release
+% decisions from one period to the next.
 %
@@
 \begin{definition}
-  We define the time span $\ts$ of the manufacturing system under investigation as
+  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
+  % with the periodised demand $\dper{\cdot}$
+  under investigation as
   \begin{align*}
-    \ts \defsym \MS[t]{\text{seasonal stuff todo}} + \z \cdot 2 \sigma \tcom
+    \ts(p) \defsym 1 + \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}} +
+    \MS[t]{\text{seasonal stuff todo}} \tcom
   \end{align*}
-  where $\z$ is a parameter.
+  where $\zs$ is a scaling parameter for specifying the confidence interval being considered. This
+  definition assumes a symmetric probability distribution of $\X$ in the second term. For asymmetric
+  probability distributions, the definition can be easily extended to integrate
 \end{definition}
+
+The reduce the impact of outliers we average the actual releases over $k$ values.
 

### 2018-10-04 paper/paper.tex
improvement of time span definition

@@
 % \usepackage{graphicx}
+
+\usepackage{mathtools}
+\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
+
 \usepackage{paper}
@@
   \begin{align*}
-    \ts(p) \defsym 1 + \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}} +
+    \ts(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
     \MS[t]{\text{seasonal stuff todo}} \tcom
   \end{align*}
-  where $\zs$ is a scaling parameter for specifying the confidence interval being considered. This
-  definition assumes a symmetric probability distribution of $\X$ in the second term. For asymmetric
-  probability distributions, the definition can be easily extended to integrate
+  where $\zs$ can be used to scale the confidence interval being considered.
+  % This
+  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
+  % to the ceiling function
+  % For asymmetric
+  % probability distributions, the definition can be easily extended to integrate
+
 \end{definition}

### 2018-10-04 paper/paper.tex
def LTS

@@
 \item Lead Time Syndrome (\LTS{})
-\item Work-in-process (\WIP{})
+\item Work-in-process (\WIP{})\\
 \end{itemize}
+
+Definition LTS~\citep{selccuk2013adaptive}: dynamic quoting of lead times $\rightarrow$ lumpy releases $\rightarrow$ larger
+WIP $\rightarrow$ longer lead times $\rightarrow$ more releases\\
 
@@
   \end{align*}
-  where $\zs$ can be used to scale the confidence interval being considered.
+  where $\zs$ can be used to select the confidence interval being considered.
   % This
@@
 
-The reduce the impact of outliers we average the actual releases over $k$ values.
+The reduce the impact of outliers we average the actual releases over $ts(p)$ values.
 

### 2018-10-04 paper/paper.tex
update

@@
   $\size{\Q_{i}} \defsym \sum_{i=1}^{n} \size{\q_{i}}$, where $n$ is the number of work-stations of stage
-  $i$. Note that in this subsection we set $i=1$.
+  $i$. Note that for this subsection $i=1$.
 
@@
 \begin{definition}
-  We define the \emph{time span} $\ts(p)$ in period $p$ of the manufacturing system
+  We define the \emph{time span considered} $\tsc(p)$ in period $p$ of the manufacturing system
   % with the periodised demand $\dper{\cdot}$
@@
   \begin{align*}
-    \ts(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
-    \MS[t]{\text{seasonal stuff todo}} \tcom
+    \tsc(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
+    \MS[t]{\text{seasonal stuff}} \tcom
   \end{align*}
-  where $\zs$ can be used to select the confidence interval being considered.
+  where $\zs$ can be used to select the confidence interval being considered. Thus under the
+  assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule, $68.3\%$,
+  $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$,
+  and $3$ respectively.
   % This
@@
 
-The reduce the impact of outliers we average the actual releases over $ts(p)$ values.
+The reduce the impact of outliers we average the actual releases over $\tsc{p}$ values.
 

### 2018-10-05 paper/paper.tex
proof lemma

@@
 
-The higher the standard deviation of the demand, the more likely it is to find high fluctuations in
-the release pattern. Thus, the scaled deviations in the demand specify a natural lower-bound of
+\begin{lemma}
+
+  % stddev(rel1) > stddev(rel0) -> stddev(dem1) > stddev(dem0)
+  It is sensible to increase the standard deviation in the release pattern if the standard deviation
+  in the demand increases.
+
+\end{lemma}
+
+\begin{proof}{Proof by induction on the size of the deviations.}
+  Wlog assume sufficient capacity for the single-stage manufacturer.
+  % Base: stddev(rel1) > 0 -> stddev(dem1) > 0
+  In case of a constant
+  demand pattern, the only sensible release pattern is to release s.t. an over the time (nearly)
+  constant output in the magnitude of the demand is achieved.
+  % or the maximum achievable constant throughput.
+  Any other release pattern will increase either back-orders or finished goods inventory and thus
+  costs. Similarly the costs increase once variability in the demand is introduced, as possible
+  unforeseen fluctuations in the demand require either to increase the stock level or accept
+  back-order costs.
+  %
+  % IH: stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
+  In case the demand deviation increases by any magnitude greater $0$, chances for the demand
+  quantities further away from the mean are increased with probability $p>0$. Thus the planner has
+  to decide whether to release additional quantity to be able to serve the demand which is more
+  likely with probability $p$. Clearly, this increases chances for either inventory costs or
+  back-order costs according to the decision of the planner and compared to the previous situation.
+  \qed
+
+  % Demand with higher stddev
+  % ----
+  % ---
+  % --
+  % ---
+  % ----
+
+  % Demand with lower stddev
+  % ---
+  % ---
+  % ---
+  % ---
+  % ---
+
+\end{proof}
+
+Put differently, for higher standard deviation in the demand higher fluctuations in the release
+pattern are sensible. Thus, the scaled deviations in the demand specify a natural lower-bound of
 release decisions to consider in the analysis of the \LTS{}.
@@
 Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
-demand as measure for determining the time span being considered. Recall that the standard deviation
-measures the expected deviation of the mean in orders.
+demand as measure for determining the time span of the release decisions and \WIP{}-levels being
+considered in the analysis. Recall that the standard deviation measures the expected deviation of
+the mean in orders.
 %

### 2018-10-05 paper/paper.tex
lemma 1

@@
 correct, however theoretically the interconnection between \WIP{}-level and number of releases is
-not needed to infer this systematic releasing misbehavior.
+not needed to infer this systematic releasing misbehavior. The dynamic quoting of the lead time can
+rather be seen as origin and perpetuating factor for the \LTS{} in practical situations.
+
+\begin{lemma}
+  The interconnection between \WIP{}-level (and also lead time for that sake), and the release
+  pattern is not necessary to observe the systematic releasing misbehavior called lead time
+  syndrome.
+\end{lemma}
 
@@
   increases the number of orders to be released on every release decision, e.g.~by 1 order. Clearly
-  the release decision does neither depend on the flow time nor lead time. However, considered over
-  time this leads to a monotonically increasing \WIP{}-level which again leads to a monotonically
-  increasing lead time.\qed
+  the release decision does neither depend on the flow time nor the lead time. However, considered
+  over time this leads to a monotonically increasing \WIP{}-level which again leads to a
+  monotonically increasing lead time. This cycle of larger \WIP{}, longer lead time, and increasing
+  amount of released orders is commonly known as lead time syndrome. \qed
 \end{proof}
@@
 
-  % stddev(rel1) > stddev(rel0) -> stddev(dem1) > stddev(dem0)
-  It is sensible to increase the standard deviation in the release pattern if the standard deviation
-  in the demand increases.
+  % stddev(dem1) > stddev(dem0) -> stddev(rel1) > stddev(rel0)
+
+  Let $p \in \Nat$ be the periods. Suppose, the deviations of the mean demand are drawn by $\X_{0}$,
+  $\X_{1}$ and the corresponding release pattern follow the random variables $\Lambda_{0}$ and
+  $\Lambda_{1}$ respectively.
+  % and the standard deviation $\stddev$ over a set of discrete
+  Then, if $\stddev(\X_{1}) > \stddev(\X_{0})$  then $\stddev(\Lambda_{1}) > \stddev(\Lambda_{0})$
+  is sensible.
+  %
+  Informally this means that for higher standard deviation in the demand a higher standard deviation
+  in the release pattern is sensible.
+
+  % It is sensible to increase the standard deviation in the release pattern if the standard
+  % deviation in the demand increases.
 
@@
   Wlog assume sufficient capacity for the single-stage manufacturer.
-  % Base: stddev(rel1) > 0 -> stddev(dem1) > 0
-  In case of a constant
-  demand pattern, the only sensible release pattern is to release s.t. an over the time (nearly)
-  constant output in the magnitude of the demand is achieved.
+  % Base: stddev(dem1) > 0 -> stddev(rel1) > 0
+  In case of a constant demand pattern, the only sensible release pattern is to release s.t. an over
+  the time (nearly) constant output in the magnitude of the demand is achieved.
   % or the maximum achievable constant throughput.
@@
 
-Put differently, for higher standard deviation in the demand higher fluctuations in the release
-pattern are sensible. Thus, the scaled deviations in the demand specify a natural lower-bound of
-release decisions to consider in the analysis of the \LTS{}.
+% The above lemma thus specifies that for higher standard deviation in the demand higher fluctuations
+% in the release pattern are sensible.
+Thus, the scaled deviations in the demand specify a natural
+lower-bound of release decisions to consider in the analysis of the \LTS{}.
 %
@@
 demand as measure for determining the time span of the release decisions and \WIP{}-levels being
-considered in the analysis. Recall that the standard deviation measures the expected deviation of
-the mean in orders.
+considered in the analysis.
+%
+% Recall that the standard deviation measures the expected deviation of
+% the mean in orders.
 %
@@
 \begin{definition}
-  We define the \emph{time span considered} $\tsc(p)$ in period $p$ of the manufacturing system
+  We define the \emph{time span considered} $\tsc{p}$ in period $p$ of the manufacturing system
   % with the periodised demand $\dper{\cdot}$
@@
   \begin{align*}
-    \tsc(p) \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
+    \tsc{p} \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
     \MS[t]{\text{seasonal stuff}} \tcom
   \end{align*}
-  where $\zs$ can be used to select the confidence interval being considered. Thus under the
-  assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule, $68.3\%$,
-  $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$,
-  and $3$ respectively.
+  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
+  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
+  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
+  $3$ respectively.
   % This

### 2018-10-05 paper/paper.tex
definitions mean demand deviation and average release quantity

@@
 \begin{lemma}
-  The interconnection between \WIP{}-level (and also lead time for that sake), and the release
-  pattern is not necessary to observe the systematic releasing misbehavior called lead time
+  The interconnection between \WIP{}-level (and thus also the lead time for that sake), and the
+  release pattern is not necessary to observe the systematic releasing misbehavior called lead time
   syndrome.
@@
 % in the release pattern are sensible.
-Thus, the scaled deviations in the demand specify a natural
+Thus, the deviations of the demand in relation to the mean specify a proportional % natural
 lower-bound of release decisions to consider in the analysis of the \LTS{}.
 %
-Hence, we use the standard deviation $\sigma$ of the random variable $\X$ in relation to the mean
-demand as measure for determining the time span of the release decisions and \WIP{}-levels being
-considered in the analysis.
+Hence, we use the standard deviation $\sigma$ of the random variable $\X$ related to the mean demand
+as measure for determining the time span of the release decisions and \WIP{}-levels being considered
+in the analysis.
 %
@@
 %
+
+\MS{2 definitions. 1. How many periods to average using $\sigma$. 2. How many periods to look back
+  for the time: season length. }
+
+\begin{definition}
+  We define the \emph{\mddname{}} $\mdd{p}$ of period $p$ and the manufacturing system
+  % with the periodised demand $\dper{\cdot}$
+  under investigation as
+  \begin{align*}
+    \mdd{p} \defsym 1 +
+    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}  +
+    \frac{\max \{|f(i)-f(i+1)|\ \mid \ \forall 0 \leqslant i \leqslant p \}}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
+  \end{align*}
+  where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
+  under the assumption of a normal distribution and according to the $68$--$95$--$99.7$ rule,
+  $68.3\%$, $95.5\%$, or $99.7\%$ of the demand deviation are used by setting $\zs$ to $1$, $2$, and
+  $3$ respectively.
+  % This
+  % definition assumes a symmetric probability distribution of $\X$ in the second term. However,  due
+  % to the ceiling function
+  % For asymmetric
+  % probability distributions, the definition can be easily extended to integrate
+\end{definition}
+
+\begin{definition}
+  The \emph{\avgrqname} $\avgrq{p}$ of period $p$ is defined as
+  \begin{align*}
+    \avgrq{p} \defsym \frac{1}{K} \cdot \sum_{i=p-K}^{p-1}{ \ri{i}{i+1} }\tcom
+  \end{align*}
+
+  where $K=\min(p,\ceil{\mdd{p}})$.
+\end{definition}
+
+\MS{TODO: same for \WIP{}}
+
+Intuitively the \mddname{} is a measure of variability and shift of the mean in the demand stream
+with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
+\mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
+\textsl{\mddname{}}-average slopes over time.
+
+% Maybe here an example?
+
+However,
+
+This time factor
+
 Futhermore,... \MS[t]{seasonal stuff}
@@
 \begin{definition}
-  We define the \emph{time span considered} $\tsc{p}$ in period $p$ of the manufacturing system
+  We define the \emph{time span} $\ts{p}$ in period $p$ of the manufacturing system
   % with the periodised demand $\dper{\cdot}$
@@
   \begin{align*}
-    \tsc{p} \defsym 1 + \ceil[\Bigg]{\frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=0}^{p}{f(i)}}} +
+    \ts{p} \defsym 1 + % \ceil[\Bigg]{
+    \frac{ \zs \cdot 2 \sigma}{\frac{1}{p} \cdot \sum_{i=1}^{p}{f(i)}}
+    % }
+    +
     \MS[t]{\text{seasonal stuff}} \tcom
@@
   % probability distributions, the definition can be easily extended to integrate
-
 \end{definition}
 
-The reduce the impact of outliers we average the actual releases over $\tsc{p}$ values.
+To reduce the impact of outliers we average the actual releases over $\ts{p}$ values.
 

### 2018-10-10 paper/paper.tex
update paper

@@
 \ARTICLEAUTHORS{%
-  \AUTHOR{Manuel Schneckenreither% \orcidID{0000-0002-4812-4665}
+  \AUTHOR{Manuel Schneckenreither%
+    % \orcidID{0000-0002-4812-4665}
+    % , Stefan Haeussler
+    % \orcidID{0000-0003-2589-1367}
   }
   \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
-  \EMAIL{manuel.schneckenreither@uibk.ac.at}} %, \URL{}}
+    \EMAIL{manuel.schneckenreither@uibk.ac.at}
+    \EMAIL{stefan.haeussler@uibk.ac.at}
+  } %, \URL{}}
 
-  \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
-  }
-  \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
-  \EMAIL{stefan.haeussler@uibk.ac.at}}
+  % \AUTHOR{Stefan Haeussler % \orcidID{0000-0003-2589-1367}
+  % }
+  % \AFF{Department of Information Systems, Production and Logistics Management, University of Innsbruck, Austria
+  % \EMAIL{stefan.haeussler@uibk.ac.at}}
 } % end of the block
@@
 In practise the available demand data is used to infer the function $\dmean$ and the value for
-$\sigma$. This could be done using regression and statistical analyses. Therefore, in hereafter
-these values are expected to be known.
+$\sigma$. This is done using regression and other statistical analyses. Therefore, hereafter the
+function $\dmean$ and the value for $\sigma$ % these values
+are expected to be known. In the following we will use these values to infer important time
+information for the analysis of the \LTS{}.
 
@@
 
-  Let $p \in \Nat$ be the periods. Suppose, the deviations of the mean demand are drawn by $\X_{0}$,
-  $\X_{1}$ and the corresponding release pattern follow the random variables $\Lambda_{0}$ and
-  $\Lambda_{1}$ respectively.
+  Let $p \in \Nat$ be the periods. Consider two demand streams where the deviations of the mean
+  demand are drawn by $\X_{0}$, $\X_{1}$ and the corresponding release pattern follow the random
+  variables $\Lambda_{0}$ and $\Lambda_{1}$ respectively.
   % and the standard deviation $\stddev$ over a set of discrete
@@
   \end{align*}
+  \MS{maybe use moving average for mean. Imagine a demand jump from bottom to top and vice versa! should
+    be equal? }
   where $\zs$ can be used to select the confidence interval of the underlying distribution. Thus
@@
 
-Intuitively the \mddname{} is a measure of variability and shift of the mean in the demand stream
-with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
+Intuitively the \mddname{} is a measure of variability and maximum leap of the mean in the demand
+stream with respect to the average mean demand and equipped with a lower-bound of $1$. We use the
 \mddname{} to average the number of releases and \WIP{}-levels to be able to investigate their
-\textsl{\mddname{}}-average slopes over time.
+\textsl{\mddname{}}-average slopes.
 
 % Maybe here an example?
-
-However,
-
-This time factor
+We compare these slopes to the slopes from the past. The amount of time which is looked into the
+past is defined by the defined by the length of the season.
 
